### 2022-04-15 Proposal/tex/proposal.tex
first

\documentclass{article}
\usepackage[preprint]{neurips_2022}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\bibliographystyle{plain}

\title{Machine Learning - Final Project Proposal}

\author{%
  Isaac Wasserman\\
  Department of Computer Science\\
  Haverford College\\
  Haverford, PA 19041\\
  \texttt{iwasserman@haverford.edu} \\
}

\begin{document}

  \maketitle

  \section{Proposal}
  For my final project, I will explore the use of generative adversarial networks (GANs) for data augmentation. Although GANs are most popularly used for domain transfer, the same basic architecture is also a good candidate for a data augmentation strategy called hallucination in which new (fake) training examples based on a small number of existing (real) examples. Though theoretically, the addition of these fake examples should not improve the performance of a discriminative model (since they can be no more representative of the true distribution than the examples they are based on), empirical studies have observed accuracy improvements on multi-class classification of up to 13\% on benchmark low-resource datasets such as Omniglot \cite{antoniou}. Data hallucination has been shown to improve performance, even without GANs; for example, randomized stem hallucination can improve the accuracy of morphological inflection models on low-resource languages by up to 76\% \cite{anastasopoulos-neubig-2019-pushing}. Surely, there is something to this strategy.

  I will start by implementing a simple GAN for the hallucination of a simple image dataset like MNIST; this process will allow me to become familiar with the technique in a medium that I can easily interpret. I then plan to test GAN based hallucination on the morphological inflection model built by Anastasopoulos and Neubig, replacing their largely randomized method with one that better models the phonotactics of the language. The dataset they used was published as part of the SIGMORPHON 2018 shared task \cite{sigmorphon}, and it includes subsets for 58 language pairs\footnote{The Anastasopoulos and Neubig model was built to be trained first on a high-resource language and then fine-tuned for a low-resource language with similar genealogy or morphological features} and 91 individual languages.

  Acknowledging the possibility that this may be more than I can accomplish in the given timeframe, I may end up needing to forgo the application of GAN hallucination to the inflection model and instead apply it to a simpler image classification task. In this case, I would first test traditional data augmentation methods and compare the effects to those of GAN hallucination.

  \section{Timeline}
    April 6th through April 15th:
    \begin{itemize}
      \item{Learn more about GANs}
      \item{Learn more about data augmentation}
    \end{itemize}
    April 16th through May 1st:
    \begin{itemize}
      \item{Implement a simple GAN for fake MNIST example generation}
      \item{Collect baseline and random hallucination accuracies for Anastasopoulos and Neubig model}
    \end{itemize}
    May 2nd through May 13th:
    \begin{itemize}
      \item{Implement GAN hallucinator to replace random hallucinator}
      \item{Write report}
    \end{itemize}
  \bibliography{sources}

\end{document}

### 2022-05-05 Proposal/tex/proposal.tex
word_gan progress

@@
   I will start by implementing a simple GAN for the hallucination of a simple image dataset like MNIST; this process will allow me to become familiar with the technique in a medium that I can easily interpret.
+Using a small subset of this dataset, I will test the effects of the addition of augmented data on a good out-of-the-box classifier (likely Adaboost) as well as a well known few-shot classification \cite{fewshot} architecture (likely a matching or twin network) \cite{matching-networks} \cite{twin-networks}.
 I then plan to test GAN based hallucination on the morphological inflection model built by Anastasopoulos and Neubig, replacing their largely randomized method with one that better models the phonotactics of the language.
@@
 In this case, I would first test traditional data augmentation methods and compare the effects to those of GAN hallucination.
+
+  \section{Related work}
+    The performance gains realized by Antoniou et al.
+\cite{antoniou} are supported by a fairly extensive body of similar evidence-based studies on data augmentation in low-resource settings.
+These studies are, more often than not, concerned with medical imaging, in which segmentation is a more salient issue than classification.
+
+    Shin et al., 2018 \cite{shin} leveraged the popular Pix2Pix \cite{pix2pix} architecture to augment a brain-tumor segmentation dataset.
+This task was considerably more complex as it involved the hallucination of image pairs.
+However, training their segmentation model on a combination of real and fake data, they observed performance improvements of up to 16\% over unaugmented data (minimum improvement of ~1\%).
+They also tested the effects of an entirely synthetic dataset; however, this resulted in a significant loss of performance compared to the baseline.
+Despite the improvements realized compared to their baseline segmentor, even their best model was unable to outperform the best-in-class reference model \cite{wang}.
+
+    Sandfort et al., 2019 \cite{sandfort} carried out a similar study using the also popular CycleGAN architecture \cite{cyclegan} to segment anomolous CT scans of kidneys, livers, and spleens.
+On average, this study showed no appreciable difference between the performance gains afforded by traditional augmentation and GAN-based augmentation.
+However, when the resulting models were tested on images that were out-of-distribution\footnote{While the training set was based on CTs with contrast, these out-of-distribution images came from scans performed without contrast.}, they found that while the baseline model scored 0.101, the traditionally augmented and GAN augmented models received scores of 0.535 and 0.747 respectively.
+This increased flexibility is interesting as it suggests that the augmented examples constitute a wider domain than the examples they are based on.
+From a theoretical standpoint, this would have to be possible if GAN augmented datasets were to outperform others.
+
+    While all of the other related works cited have used GANs to create synthetic image data, Gupta, 2019 \cite{gupta} applies GAN-based augmentation to language data for the purpose of sentiment analysis.
+Unlike the other applications, labeled language data for sentiment analysis is not scarce.
+The datasets used each contain between 2000 and 4000 real examples, and the classifier was pre-trained on a dataset of over 1.6 million examples.
+Real and fake examples were combined in a somewhat nontraditional way; instead of concatenating the real and synthetic datasets, separate classifiers were trained for each and their outputs were combined via bagging.
+In these experiments, accuracy was only improved by up to 1.2\% when fake examples were added.
+Though these gains are less impressive than others cited above, these results support the idea that GAN-based augmentation can be applied to domains outside of image data.
 
@@
     \end{itemize}
+
   \bibliography{sources}

### 2022-05-05 MNIST_GAN/augment.py

@@ -1,0 +1,143 @@
+
+import align
+import argparse
+import codecs
+import os, sys
+from random import random, choice
+import re
+
+
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
+    for l in lines:
+        l = l.strip().split('\t')
+        if l:
+            inputs.append(list(l[0].strip()))
+            outputs.append(list(l[1].strip()))
+            tags.append(re.split('\W+', l[2].strip()))
+    return inputs, outputs, tags
+
+def find_good_range(a,b):
+	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	if sum(mask) == 0:
+		# Some times the alignment is off-by-one
+		b = ' ' + b
+		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	ranges = []
+	prev = False
+	for i,k in enumerate(mask):
+		if k and prev:
+			prev = True
+		elif k and not prev:
+			start = i
+			prev = True
+		elif prev and not k:
+			end = i
+			ranges.append((start, end))
+			prev = False
+		elif not prev and not k:
+			prev = False
+	if prev:
+		ranges.append((start,i+1))
+	ranges = [c for c in ranges if c[1]-c[0]>2]
+	return ranges
+
+
+def augment(inputs, outputs, tags, characters):
+	temp = [(''.join(inputs[i]), ''.join(outputs[i])) for i in range(len(outputs))]
+	aligned = align.Aligner(temp).alignedpairs
+	# print(aligned)
+
+	vocab = list(characters)
+	try:
+		vocab.remove(u" ")
+	except:
+		pass
+
+	new_inputs = []
+	new_outputs = []
+	new_tags = []
+	for k,item in enumerate(aligned):
+		#print(''.join(inputs[k]) + '\t' + ''.join(outputs[k]))
+		i,o = item[0],item[1]
+		good_range = find_good_range(i,o)
+		#print(good_range)
+		if good_range:
+			new_i, new_o = list(i), list(o)
+			for r in good_range:
+				s = r[0]
+				e = r[1]
+				if (e-s>5): #arbitrary value
+					s += 1
+					e -= 1
+				for j in range(s,e):
+					if random() > 0.5: #arbitrary value
[…]

### 2022-05-05 word_gan/losses_impl.py
switched to wasserstein loss

@@ -1,0 +1,1101 @@
+# coding=utf-8
+# Copyright 2022 The TensorFlow GAN Authors.
+#
+# Licensed under the Apache License, Version 2.0 (the "License");
+# you may not use this file except in compliance with the License.
+# You may obtain a copy of the License at
+#
+#     http://www.apache.org/licenses/LICENSE-2.0
+#
+# Unless required by applicable law or agreed to in writing, software
+# distributed under the License is distributed on an "AS IS" BASIS,
+# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
+# See the License for the specific language governing permissions and
+# limitations under the License.
+
+"""Losses that are useful for training GANs.
+
+The losses belong to two main groups, but there are others that do not:
+1) xxxxx_generator_loss
+2) xxxxx_discriminator_loss
+
+Example:
+1) wasserstein_generator_loss
+2) wasserstein_discriminator_loss
+
+Other example:
+wasserstein_gradient_penalty
+
+All losses must be able to accept 1D or 2D Tensors, so as to be compatible with
+patchGAN style losses (https://arxiv.org/abs/1611.07004).
+
+To make these losses usable in the TF-GAN framework, please create a tuple
+version of the losses with `losses_utils.py`.
+"""
+
+import tensorflow as tf
+
+
+def _to_float(tensor):
+  return tf.cast(tensor, tf.float32)
+
+
+# Wasserstein losses from `Wasserstein GAN` (https://arxiv.org/abs/1701.07875).
+def wasserstein_generator_loss(
+    discriminator_gen_outputs,
+    weights=1.0,
+    scope=None,
+    loss_collection=tf.compat.v1.GraphKeys.LOSSES,
+    reduction=tf.compat.v1.losses.Reduction.SUM_BY_NONZERO_WEIGHTS,
+    add_summaries=False):
+  """Wasserstein generator loss for GANs.
+
+  See `Wasserstein GAN` (https://arxiv.org/abs/1701.07875) for more details.
+
+  Args:
+    discriminator_gen_outputs: Discriminator output on generated data. Expected
+      to be in the range of (-inf, inf).
+    weights: Optional `Tensor` whose rank is either 0, or the same rank as
+      `discriminator_gen_outputs`, and must be broadcastable to
+      `discriminator_gen_outputs` (i.e., all dimensions must be either `1`, or
+      the same as the corresponding dimension).
+    scope: The scope for the operations performed in computing the loss.
[…]

### 2022-05-06 word_gan/train.py
finished bengali, started breton, syriac, cornish, crimean tatar

@@ -1,0 +1,312 @@
+import numpy as np
+import tensorflow as tf
+import tensorflow.keras as keras
+from tensorflow.keras import layers
+from keras.preprocessing import sequence
+from sklearn.model_selection import train_test_split
+import pandas as pd
+
+import align
+import argparse
+import codecs
+import os, sys
+from random import random, choice
+import re
+import glob
+import matplotlib.pyplot as plt
+import time
+from losses_impl import *
+from keras import backend
+
+
+from IPython.utils import io
+max_stem_length = 10
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
+    for l in lines:
+        l = l.strip().split('\t')
+        if l:
+            inputs.append(list(l[0].strip()))
+            outputs.append(list(l[1].strip()))
+            tags.append(re.split('\W+', l[2].strip()))
+    return inputs, outputs, tags
+
+def find_good_range(a,b):
+	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	if sum(mask) == 0:
+		# Some times the alignment is off-by-one
+		b = [' '] + b
+		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	ranges = []
+	prev = False
+	for i,k in enumerate(mask):
+		if k and prev:
+			prev = True
+		elif k and not prev:
+			start = i
+			prev = True
+		elif prev and not k:
+			end = i
+			ranges.append((start, end))
+			prev = False
+		elif not prev and not k:
+			prev = False
+	if prev:
+		ranges.append((start,i+1))
+	ranges = [c for c in ranges if c[1]-c[0]>2]
+	return ranges
+def generate_stem():
+	return "___"
+
+def get_chars(l):
+    flat_list = [char for word in l for char in word]
+    return list(set(flat_list))
+def best_range(ranges):
+    longest_length = 0
+    longest_index = 0
+    for i,r in enumerate(ranges):
+        length = r[1] - r[0]
+        if length > longest_length:
+            longest_length = length
+            longest_index = i
+    return ranges[i]
+
+def augment(input_path):
+    inputs,outputs,tags = np.array(read_data(input_path), dtype=object)
+    temp = [(''.join(inputs[i]), ''.join(outputs[i])) for i in range(len(outputs))]
+    aligned = align.Aligner(temp).alignedpairs
[…]

### 2022-05-07 word_gan/align.c
resigned

@@ -1,0 +1,711 @@
+/************************************************************************/
+/*   crpalign - Chinese Restaurant Process string pair aligner          */
+/*   Copyright © 2013 Mans Hulden                                       */
+/*                                                                      */
+/*   This file is part of crpalign.                                     */
+/*                                                                      */
+/* Licensed under the Apache License, Version 2.0 (the "License");      */
+/* you may not use this file except in compliance with the License.     */
+/* You may obtain a copy of the License at                              */
+/*                                                                      */
+/*     http://www.apache.org/licenses/LICENSE-2.0                       */
+/*                                                                      */
+/************************************************************************/
+
+/* To build python bindings: gcc -O3 -Wall -Wextra -shared align.c -o libalign.so */
+/* WARNING: currently not thread-safe */
+
+#include <stdio.h>
+#include <string.h>
+#include <stdlib.h>
+#include <time.h>
+#include <math.h>
+#include <stdarg.h>
+#include <unistd.h>
+#include <getopt.h>
+
+/* Yields minimum of three values */
+#define MIN3(a, b, c) ((a) < (b) ? ((a) < (c) ? (a) : (c)) : ((b) < (c) ? (b) : (c)))
+/* Compares three values, yielding -1, 0, 1 depending on if a, b, or c is the smallest */
+#define CMP3(a, b, c) ((a) < (b) ? ((a) < (c) ? (-1) : (1)) : ((b) < (c) ? (0) : (1)))
+
+#define LEFT -1
+#define DIAG  0
+#define DOWN  1
+
+#define INPUT_FORMAT_L2P  0
+#define INPUT_FORMAT_NEWS 1
+
+#define OUTPUT_FORMAT_PLAIN         0
+#define OUTPUT_FORMAT_ALIGNED       1
+#define OUTPUT_FORMAT_PHONETISAURUS 2
+#define OUTPUT_FORMAT_M2M           3
+
+#define MATRIX_MODE_MED   0
+#define MATRIX_MODE_GS    1
+
[…]

### 2022-05-07 word_gan/augment.py

@@ -1,143 +1,0 @@
-
-import align
-import argparse
-import codecs
-import os, sys
-from random import random, choice
-import re
-
-
-def read_data(filename):
-    with codecs.open(filename, 'r', 'utf-8') as inp:
-        lines = inp.readlines()
-    inputs = []
-    outputs = []
-    tags = []
-    for l in lines:
-        l = l.strip().split('\t')
-        if l:
-            inputs.append(list(l[0].strip()))
-            outputs.append(list(l[1].strip()))
-            tags.append(re.split('\W+', l[2].strip()))
-    return inputs, outputs, tags
-
-def find_good_range(a,b):
-	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
-	if sum(mask) == 0:
-		# Some times the alignment is off-by-one
-		b = ' ' + b
-		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
-	ranges = []
-	prev = False
-	for i,k in enumerate(mask):
-		if k and prev:
-			prev = True
-		elif k and not prev:
-			start = i
-			prev = True
-		elif prev and not k:
-			end = i
-			ranges.append((start, end))
-			prev = False
-		elif not prev and not k:
-			prev = False
-	if prev:
-		ranges.append((start,i+1))
-	ranges = [c for c in ranges if c[1]-c[0]>2]
-	return ranges
-
-
-def augment(inputs, outputs, tags, characters):
-	temp = [(''.join(inputs[i]), ''.join(outputs[i])) for i in range(len(outputs))]
-	aligned = align.Aligner(temp).alignedpairs
-	# print(aligned)
-
-	vocab = list(characters)
-	try:
-		vocab.remove(u" ")
-	except:
-		pass
-
-	new_inputs = []
-	new_outputs = []
-	new_tags = []
-	for k,item in enumerate(aligned):
-		#print(''.join(inputs[k]) + '\t' + ''.join(outputs[k]))
-		i,o = item[0],item[1]
-		good_range = find_good_range(i,o)
-		#print(good_range)
-		if good_range:
-			new_i, new_o = list(i), list(o)
-			for r in good_range:
-				s = r[0]
-				e = r[1]
-				if (e-s>5): #arbitrary value
-					s += 1
-					e -= 1
-				for j in range(s,e):
-					if random() > 0.5: #arbitrary value
[…]

### 2022-05-07 word_gan/smart_augment.py

@@ -1,0 +1,393 @@
+
+import align
+import argparse
+import codecs
+import os, sys
+from random import random, choice
+import re
+
+import numpy as np
+import tensorflow as tf
+import tensorflow.keras as keras
+import glob
+
+from keras.preprocessing import sequence
+from IPython.utils import io
+from sklearn.model_selection import train_test_split
+
+parser = argparse.ArgumentParser()
+parser.add_argument("datapath", help="path to data", type=str)
+parser.add_argument("language", help="language", type=str)
+parser.add_argument("epoch", help="which model epoch to use", type=str, default=1500)
+parser.add_argument("--examples", help="number of hallucinated examples to create (def: 10000)", default=10000, type=int)
+parser.add_argument("--use_dev", help="whether to use the development set (def: False)", action="store_true")
+args = parser.parse_args()
+
+DATA_PATH = args.datapath
+L2 = args.language
+model_epoch = args.epoch
+
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
+    for l in lines:
+        l = l.strip().split('\t')
+        if l:
+            inputs.append(list(l[0].strip()))
+            outputs.append(list(l[1].strip()))
+            tags.append(re.split('\W+', l[2].strip()))
+    return inputs, outputs, tags
+
+def find_good_range(a,b):
+	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	if sum(mask) == 0:
+		# Some times the alignment is off-by-one
+		b = ' ' + b
+		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	ranges = []
+	prev = False
+	for i,k in enumerate(mask):
+		if k and prev:
+			prev = True
+		elif k and not prev:
+			start = i
+			prev = True
+		elif prev and not k:
+			end = i
+			ranges.append((start, end))
+			prev = False
+		elif not prev and not k:
+			prev = False
+	if prev:
+		ranges.append((start,i+1))
+	ranges = [c for c in ranges if c[1]-c[0]>2]
+	return ranges
+
+
+
+max_stem_length = 10
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
[…]

### 2022-05-09 word_gan/augment_ngram.py
progress

@@ -18,7 +18,7 @@ from sklearn.model_selection import train_test_split
 parser = argparse.ArgumentParser()
 parser.add_argument("datapath", help="path to data", type=str)
 parser.add_argument("language", help="language", type=str)
-parser.add_argument("epoch", help="which model epoch to use", type=str, default=1500)
+parser.add_argument("--epoch", help="which model epoch to use", type=str, default=1500, required=False)
 parser.add_argument("--examples", help="number of hallucinated examples to create (def: 10000)", default=10000, type=int)
 parser.add_argument("--use_dev", help="whether to use the development set (def: False)", action="store_true")
 args = parser.parse_args()
@@ -279,10 +279,9 @@ def create_single_language_stem_dataset(language, hilo="high"):
     X,lut = one_hot_encode_sequence(reference_stems, combined_vocab)
     labels = np.array([1] * len(reference_stems))
     X_train, X_test, y_train, y_test = train_test_split(X, labels, test_size=0.001)
-    return X_train, X_test, y_train, y_test, combined_vocab, lut
+    return ["".join(stem).replace("0","") for stem in reference_stems]
 
 language = L2
-X_train, X_test, y_train, y_test, X_vocab, lut = create_single_language_stem_dataset(language, hilo="low")
 
 
 
@@ -294,23 +293,20 @@ def wasserstein_loss(y_true, y_pred):
     y_pred_adjusted = tf.math.subtract(tf.math.multiply(y_pred, 2), 1)
     return backend.mean(y_true_adjusted * y_pred_adjusted)
 
-hallucinator = keras.models.load_model(f'checkpoints/{language}-epoch-{model_epoch}.h5',custom_objects={"wasserstein_loss":wasserstein_loss})
-generator = keras.models.Sequential([hallucinator.layers[0]])
-generator.build(input_shape=[1,10,32])
-generator.summary()
-def hallucinate_stem(original):
-	seq = "".join([lut[np.argmax(onehot)] for onehot in distribution_to_sequence(generator(tf.random.normal(shape=[1,10,32]))[0])])
-	if "0" in seq:
-		seq = seq[:seq.index("0")]
-	# remove reduplication
-	new_seq = ""
-	for i,char in enumerate(seq):
-		if seq[i] != seq[i-1] and seq[i] != "0":
-			new_seq = new_seq + char
[…]

### 2022-05-09 word_gan/augment_regular.py

@@ -1,0 +1,143 @@
+
+import align
+import argparse
+import codecs
+import os, sys
+from random import random, choice
+import re
+
+
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
+    for l in lines:
+        l = l.strip().split('\t')
+        if l:
+            inputs.append(list(l[0].strip()))
+            outputs.append(list(l[1].strip()))
+            tags.append(re.split('\W+', l[2].strip()))
+    return inputs, outputs, tags
+
+def find_good_range(a,b):
+	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	if sum(mask) == 0:
+		# Some times the alignment is off-by-one
+		b = ' ' + b
+		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	ranges = []
+	prev = False
+	for i,k in enumerate(mask):
+		if k and prev:
+			prev = True
+		elif k and not prev:
+			start = i
+			prev = True
+		elif prev and not k:
+			end = i
+			ranges.append((start, end))
+			prev = False
+		elif not prev and not k:
+			prev = False
+	if prev:
+		ranges.append((start,i+1))
+	ranges = [c for c in ranges if c[1]-c[0]>2]
+	return ranges
+
+
+def augment(inputs, outputs, tags, characters):
+	temp = [(''.join(inputs[i]), ''.join(outputs[i])) for i in range(len(outputs))]
+	aligned = align.Aligner(temp).alignedpairs
+	# print(aligned)
+
+	vocab = list(characters)
+	try:
+		vocab.remove(u" ")
+	except:
+		pass
+
+	new_inputs = []
+	new_outputs = []
+	new_tags = []
+	for k,item in enumerate(aligned):
+		#print(''.join(inputs[k]) + '\t' + ''.join(outputs[k]))
+		i,o = item[0],item[1]
+		good_range = find_good_range(i,o)
+		#print(good_range)
+		if good_range:
+			new_i, new_o = list(i), list(o)
+			for r in good_range:
+				s = r[0]
+				e = r[1]
+				if (e-s>5): #arbitrary value
+					s += 1
+					e -= 1
+				for j in range(s,e):
+					if random() > 0.5: #arbitrary value
[…]

### 2022-05-09 word_gan/augment_smart.py

@@ -1,0 +1,402 @@
+
+import align
+import argparse
+import codecs
+import os, sys
+from random import random, choice
+import re
+
+import numpy as np
+import tensorflow as tf
+import tensorflow.keras as keras
+import glob
+
+from keras.preprocessing import sequence
+from IPython.utils import io
+from sklearn.model_selection import train_test_split
+
+parser = argparse.ArgumentParser()
+parser.add_argument("datapath", help="path to data", type=str)
+parser.add_argument("language", help="language", type=str)
+parser.add_argument("epoch", help="which model epoch to use", type=str, default=1500)
+parser.add_argument("--examples", help="number of hallucinated examples to create (def: 10000)", default=10000, type=int)
+parser.add_argument("--use_dev", help="whether to use the development set (def: False)", action="store_true")
+args = parser.parse_args()
+
+DATA_PATH = args.datapath
+L2 = args.language
+model_epoch = args.epoch
+
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
+    for l in lines:
+        l = l.strip().split('\t')
+        if l:
+            inputs.append(list(l[0].strip()))
+            outputs.append(list(l[1].strip()))
+            tags.append(re.split('\W+', l[2].strip()))
+    return inputs, outputs, tags
+
+def find_good_range(a,b):
+	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	if sum(mask) == 0:
+		# Some times the alignment is off-by-one
+		b = ' ' + b
+		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
+	ranges = []
+	prev = False
+	for i,k in enumerate(mask):
+		if k and prev:
+			prev = True
+		elif k and not prev:
+			start = i
+			prev = True
+		elif prev and not k:
+			end = i
+			ranges.append((start, end))
+			prev = False
+		elif not prev and not k:
+			prev = False
+	if prev:
+		ranges.append((start,i+1))
+	ranges = [c for c in ranges if c[1]-c[0]>2]
+	return ranges
+
+
+
+max_stem_length = 10
+def read_data(filename):
+    with codecs.open(filename, 'r', 'utf-8') as inp:
+        lines = inp.readlines()
+    inputs = []
+    outputs = []
+    tags = []
+    for l in lines:
[…]

### 2022-05-09 word_gan/auto_augmentor.py

@@ -1,0 +1,11 @@
+import os
+
+languages = ["azeri","bengali","crimean-tatar","ingrian","karelian","kashubian","livonian","maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
+
+for language in languages:
+    print(f'Working on {language}, regular')
+    os.system(f'python augment_regular.py sigmorphon_data {language} --examples 10000')
+    print(f'Working on {language}, smart')
+    os.system(f'python augment_smart.py sigmorphon_data {language} 1500 --examples 10000')
+    print(f'Working on {language}, ngram')
+    os.system(f'python augment_ngram.py sigmorphon_data {language} --examples 10000')

### 2022-05-09 word_gan/augment_regular.py
finished gan training

@@ -25,7 +25,7 @@ def find_good_range(a,b):
 	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
 	if sum(mask) == 0:
 		# Some times the alignment is off-by-one
-		b = ' ' + b
+		b = [' '] + b
 		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
 	ranges = []
 	prev = False

### 2022-05-09 word_gan/auto_augmentor.py

@@ -1,7 +1,8 @@
 import os
 
 languages = ["azeri","bengali","crimean-tatar","ingrian","karelian","kashubian","livonian","maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
-
+languages = ["maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
+languages = ["livonian"]
 for language in languages:
     print(f'Working on {language}, regular')
     os.system(f'python augment_regular.py sigmorphon_data {language} --examples 10000')

### 2022-05-09 word_gan/test_augmentation.py

@@ -1,0 +1,35 @@
+import os
+import time
+
+languages = ["azeri","bengali","crimean-tatar","ingrian","karelian","kashubian","maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar","livonian"]
+
+print("start time:", time.time())
+
+progress = 0
+max_progress = len(languages * 3)
+progress_bar = "[" + "".join([" "] * max_progress) + "]"
+
+for language in languages:
+    print(f'Working on {language}, regular')
+    os.system(f'mv sigmorphon_data/{language}-hall-regular sigmorphon_data/{language}-hall')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-regular.log 2>&1')
+    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-regular')
+    os.system(f'mv models/{language} models/{language}-hall-regular')
+    progress += 1
+    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
+
+    print(f'Working on {language}, ngram')
+    os.system(f'mv sigmorphon_data/{language}-hall-ngram sigmorphon_data/{language}-hall')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-ngram.log 2>&1')
+    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-ngram')
+    os.system(f'mv models/{language} models/{language}-hall-ngram')
+    progress += 1
+    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
+
+    print(f'Working on {language}, smart')
+    os.system(f'mv sigmorphon_data/{language}-hall-smart sigmorphon_data/{language}-hall')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-smart.log 2>&1')
+    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-smart')
+    os.system(f'mv models/{language} models/{language}-hall-smart')
+    progress += 1
+    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"

### 2022-05-09 Proposal/tex/proposal.tex
working on paper

@@
-\documentclass{article}
+≈\documentclass{article}
 \usepackage[preprint]{neurips_2022}
@@
 They also tested the effects of an entirely synthetic dataset; however, this resulted in a significant loss of performance compared to the baseline.
-Despite the improvements realized compared to their baseline segmentor, even their best model was unable to outperform the best-in-class reference model \cite{wang}.
+Despite the improvements realized when compared to their baseline segmentor, even their best model was unable to outperform the best-in-class reference model \cite{wang}.
 

### 2022-05-09 tex/paper.tex
working on paper

\documentclass{article}
\usepackage[preprint]{neurips_2022}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{xcolor}         % colors
\bibliographystyle{plain}

\title{Modeling the Graphotactics of Low-Resource Languages Using Sequential GANs}

\author{%
  Isaac Wasserman\\
  Department of Computer Science\\
  Haverford College\\
  Haverford, PA 19041\\
  \texttt{iwasserman@haverford.edu} \\
}

\begin{document}

  \maketitle
  \begin{abstract}
    Generative Adversarial Networks (GANs) have been shown to aid in the creation of artificial data in situations where large amounts of real data are difficult to come by. This issue is especially salient in the computational linguistics space, where researchers are often tasked with modeling the complex morphologic and grammatical processes of low-resource languages. This paper will discuss the implementation and testing of a GAN that attempts to model and reproduce the graphotactics of a language using only 100 example strings. These artificial, yet graphotactically compliant, strings are meant to aid in modeling the morphological inflection of low-resource languages.
  \end{abstract}
  \section{Introduction}
  \subsection{Task}
  In 2019, Anastasopoulos and Neubig made waves with their multilingual morphological inflection model for low resource languages \cite{CMU} that they submitted to the SIGMORPHON 2019 shared task \cite{sigmorphon2019}. All models submitted were pretrained on high resource languages of similar ancestry to the target language, allowing many models to greatly exceed the performance of previous attempts at low-resource morphological inflection. However, what allowed Anastasopoulos and Neubig's model to outperform other submissions was its use of data ``hallucination''.

  To perform this hallucination, they aligned the lemma with its inflected form, extracted the stem, and generated new artificial examples by replacing this stem with randomly generated strings (in the language's alphabet) of equal length.\footnote{The alignment process assumes that the lemma and inflected form share a common substring.} Though a seemingly haphazard method of data augmentation, this approach allowed for an additional 10\% accuracy, on average, when tested against versions of the model that only used cross-lingual transfer.

  Surely, a more well informed approach to stem generation would further improve the accuracy of the inflectional model. Given the demonstrated ability of GANs to produce photorealistic, yet completely contrived images, they are potentially ideal for such a task.

  \subsection{Generative Adversarial Networks}
  Generative adversarial networks are a class of unsupervised machine learning architectures, most commonly used for image generation. These networks consist of a generator and a discriminator that are trained simultaneously on a set of data representing a class or domain; this domain could be anything from photos of human faces to time series of hourly temperatures.\footnote{Technically speaking, the generator and discriminator are most often trained one after another on a repeated basis.} The generator is tasked with producing ``fake'' examples that are within this domain without ever seeing any real examples from the training set. Meanwhile, the discriminator is fed a combination of fake examples (from the generator) and real examples and is tasked with classifying them as real or fake. The respective goals of the generator and discriminator constitute a zero-sum game, in which the generator is constantly trying to outsmart the discriminator, while the discriminator hones its ability to distinguish between in-domain and out-of-domain examples.

  Though GANs are most often applied to image data (as in the popular CycleGAN \cite{cyclegan}, StyleGAN \cite{stylegan}, and DiscoGAN \cite{discogan}), the same logic is also applicable to other types of data. For example, in 2017, Esteban et al. developed a pair of recurrent GANs which they applied to medical time series data \cite{rcgan}, and in 2016, Yu et al. developed a GAN architecture made specifically for sequences and language generation, utilizing techniques from reinforcement learning \cite{seqgan}.

  \subsection{GANs for Data Augmentation}
  Although GANs are most popularly used for domain transfer, the same basic architecture is also a good candidate for a data augmentation strategy called hallucination in which new (fake) training examples based on a small number of existing (real) examples.

  Though theoretically, the addition of these fake examples should not improve the performance of a discriminative model (since they can be no more representative of the true distribution than the examples they are based on), an empirical study by Antoniou et al. observed accuracy improvements on multi-class classification of up to 13\% on benchmark low-resource datasets such as Omniglot \cite{antoniou}. These performance gains are supported by a fairly extensive body of similar evidence-based studies on GAN-based data augmentation in low-resource settings. These studies are, more often than not, concerned with medical imaging, in which segmentation is a more salient issue than classification.

  Shin et al., 2018 \cite{shin} leveraged the popular Pix2Pix \cite{pix2pix} architecture to augment a brain-tumor segmentation dataset. This task was considerably more complex as it involved the hallucination of image pairs. However, training their segmentation model on a combination of real and fake data, they observed performance improvements of up to 16\% over unaugmented data (minimum improvement of ~1\%). They also tested the effects of an entirely synthetic dataset; however, this resulted in a significant loss of performance compared to the baseline. Despite the improvements realized when compared to their baseline segmentor, even their best model was unable to outperform the best-in-class reference model \cite{wang}.

  Sandfort et al., 2019 \cite{sandfort} carried out a similar study using the also popular CycleGAN architecture \cite{cyclegan} to segment anomolous CT scans of kidneys, livers, and spleens. On average, this study showed no appreciable difference between the performance gains afforded by traditional augmentation and GAN-based augmentation. However, when the resulting models were tested on images that were out-of-distribution, they found that while the baseline model scored 0.101, the traditionally augmented and GAN augmented models received scores of 0.535 and 0.747 respectively.\footnote{While the training set was based on CTs with contrast, these out-of-distribution images came from scans performed without contrast.} This increased flexibility is interesting as it suggests that the augmented examples constitute a wider domain than the examples they are based on. From a theoretical standpoint, this would have to be possible if GAN augmented datasets were to outperform others.

  While all of the other related works cited have used GANs to create synthetic image data, Gupta, 2019 \cite{gupta} applies GAN-based augmentation to language data for the purpose of sentiment analysis. Unlike the other applications, labeled language data for sentiment analysis is not scarce. The datasets used each contain between 2000 and 4000 real examples, and the classifier was pre-trained on a dataset of over 1.6 million examples. Real and fake examples were combined in a somewhat nontraditional way; instead of concatenating the real and synthetic datasets, separate classifiers were trained for each and their outputs were combined via bagging. In these experiments, accuracy was only improved by up to 1.2\% when fake examples were added. Though these gains are less impressive than others cited above, these results support the idea that GAN-based augmentation can be applied to domains outside of image data.

  \section{Method}

  \bibliography{sources}

\end{document}

### 2022-05-09 word_gan/augment_smart.py

@@ -14,6 +14,7 @@ import glob
 from keras.preprocessing import sequence
 from IPython.utils import io
 from sklearn.model_selection import train_test_split
+from alive_progress import alive_bar
 
 parser = argparse.ArgumentParser()
 parser.add_argument("datapath", help="path to data", type=str)
@@ -376,21 +377,24 @@ devi, devo, devt = read_data(DEV_PATH)
 vocab = get_chars(lowi+lowo+devi+devo)
 
 i,o,t = [], [], []
-while len(i) < N:
-	if usedev:
-		# Do augmentation also using examples from dev
-		ii,oo,tt = augment(devi+lowi, devo+lowo, devt+lowt, vocab, L2)
-	else:
-		# Just augment the training set
-		ii,oo,tt = augment(lowi, lowo, lowt, vocab, L2)
-	ii = [c for c in ii if c]
-	oo = [c for c in oo if c]
-	tt = [c for c in tt if c]
-	i += ii
-	o += oo
-	t += tt
-	if len(ii) == 0:
-		break
+
+with alive_bar(N // len(lowi), title="Smart augmentation:") as bar:
+    for k in range(N // len(lowi)):
+        if usedev:
+            # Do augmentation also using examples from dev
+            ii,oo,tt = augment(devi+lowi, devo+lowo, devt+lowt, vocab, L2)
+        else:
+            # Just augment the training set
+            ii,oo,tt = augment(lowi, lowo, lowt, vocab, L2)
+        ii = [c for c in ii if c]
+        oo = [c for c in oo if c]
+        tt = [c for c in tt if c]
+        i += ii
+        o += oo
+        t += tt
+        if len(ii) == 0:
+            break
+        bar()
 
 # Wait is this needed?
 i = [c for c in i if c]

### 2022-05-09 word_gan/auto_augmentor.py

@@ -2,7 +2,7 @@ import os
 
 languages = ["azeri","bengali","crimean-tatar","ingrian","karelian","kashubian","livonian","maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
 languages = ["maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
-languages = ["livonian"]
+languages = ["ingrian"]
 for language in languages:
     print(f'Working on {language}, regular')
     os.system(f'python augment_regular.py sigmorphon_data {language} --examples 10000')

### 2022-05-09 word_gan/test_augmentation.py

@@ -1,35 +1,0 @@
-import os
-import time
-
-languages = ["azeri","bengali","crimean-tatar","ingrian","karelian","kashubian","maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar","livonian"]
-
-print("start time:", time.time())
-
-progress = 0
-max_progress = len(languages * 3)
-progress_bar = "[" + "".join([" "] * max_progress) + "]"
-
-for language in languages:
-    print(f'Working on {language}, regular')
-    os.system(f'mv sigmorphon_data/{language}-hall-regular sigmorphon_data/{language}-hall')
-    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-regular.log 2>&1')
-    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-regular')
-    os.system(f'mv models/{language} models/{language}-hall-regular')
-    progress += 1
-    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
-
-    print(f'Working on {language}, ngram')
-    os.system(f'mv sigmorphon_data/{language}-hall-ngram sigmorphon_data/{language}-hall')
-    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-ngram.log 2>&1')
-    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-ngram')
-    os.system(f'mv models/{language} models/{language}-hall-ngram')
-    progress += 1
-    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
-
-    print(f'Working on {language}, smart')
-    os.system(f'mv sigmorphon_data/{language}-hall-smart sigmorphon_data/{language}-hall')
-    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-smart.log 2>&1')
-    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-smart')
-    os.system(f'mv models/{language} models/{language}-hall-smart')
-    progress += 1
-    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"

### 2022-05-10 tex/paper.tex
inflection training done

@@
 \usepackage{xcolor}         % colors
+\usepackage{graphicx}
+\usepackage{float}
 \bibliographystyle{plain}
@@
   \section{Method}
+    \subsection{Data Pipeline}
+      All language data used was sourced from the SIGMORPHON 2019 repository and was initially formatted according the the Unimorph schema.
+The data for each language was gathered from their respective Wikipedia.
+Only the "train-low" sets were used for training.
+These datasets has only 100 examples, with each containing a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the "train-low" sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}
 
+      To produce training data for the GAN, base forms were aligned with inflected forms using a technique developed by Mans Hulden called Chinese restaurant process alignment \cite{crpalign}.
+Based on the alignment, a series of likely stems are generated using code from Anastasopoulos and Neubig, 2019 \cite{CMU}; as most of the languages tested use primarily suffixational inflection, the first of these "likely" stems was assumed to be the true stem and was included in the language's training set as an example of graphotactic compliance.
+
+      Non-alphabetic symbols, such as punctuation, numerals, and spaces were removed from each stem.
+Although the very small training sets provided by SIGMORPHON were likely hand gathered, the data was not free of anomolous examples.
+While attempting to gauge the model's behavior on a familiar language, it was found that the English dataset contained extremely uncommon characters such as ``æ'', ``é'', ``ë'', ``ö'', and ``œ''; however, it was decided that was not necessary to exclude these characters, as the model should recognize their infrequency, even in a dataset of only 100 examples.
+
+      Finally, the stems were padded to reach a length of 10 and encoded as 10 $\times$ $len(\textrm{alphabet})$ one-hot sequences.
+
+    \subsection{Stem GAN}
+      Although proven methods exist for building GANs for sequence data such as SeqGAN \cite{seqgan}, it was decided that these models would likely be too complex and therefore prone to overfitting and vanishing gradients when trained on such a small dataset.
+Instead, a minimalally complex GAN was created (Fig.
+\ref{fig:architecture}).
+The generator took noise input of shape 10 (representing the maximum expected stem length) $\times$ $len(\textrm{alphabet})$ and consisted of two 100 unit LSTMs with $tanh$ activations, separated by a 20\% dropout layer, and concluded with a single $len(\textrm{alphabet})$ unit dense layer with softmax activation, producing an output of equal shape to the input.
+The discriminator receives this output concatenated with one real example from the training set.
+Due to signs of mode collapse in early tests with two layers, the discriminator was given just one 100 unit LSTM.
+The discriminator terminates with a sigmoid activated single unit dense layer, that outputs a predicted probability that each example is real.
+
+      \begin{figure}[H]
+        \center
+        \includegraphics[width=\linewidth]{architecture.pdf}
+        \caption{Architecture of stem the generation model}
+        \label{fig:architecture}
+      \end{figure}
+
+      The model was trained with a batch size of 1 for 1500 epochs on each low-resource language.
+After early tests resulted in mode mode collapse, the loss functions of both the discriminator and GAN as a whole were switched from binary cross entropy to Wasserstein loss \cite{wgan}.
+
+    \subsection{Augmentation and Output Cleaning}
+      The resultant models were each used to produce 10,000 artificial training examples.
+This process involved a modified version of the augmentation script from Anastasopoulos and Neubig, 2019 \cite{CMU}.
+
+      The strings produced by the resultant models were, unfortunately, not always of the correct shape.
+Some had zeroes (representing null characters) in the middle, others filled the entire 10 available characters (which most real stems do not).
+To combat this, model output strings were "cleaned".
+Strings were cut off at the first zero from the left (all languages were left-to-right), if a character was repeated more than twice consecutively, it was collapsed to just two, and if the length of the stem was longer than the real stem it was replacing, it was shortened to a matching length.
+
+    \subsection{Testing}
+
+  \section{Results}
+  \section{Discussion}
+
+  REMEMBER TO INCLUDE LINKS TO ALL CODE CREATED AND USED
   \bibliography{sources}

### 2022-05-10 inflection/inflection.py
removed submodule

@@ -1,0 +1,1602 @@
+# -*- coding: utf-8 -*-
+
+import argparse
+import codecs
+import dynet as dy
+import matplotlib 
+matplotlib.use('agg') 
+import matplotlib.pyplot as plt
+import myutil
+import numpy as np
+from operator import itemgetter
+import os, sys
+from random import random,shuffle
+import time
+from alive_progress import alive_bar
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument("--datapath", help="path to data", type=str, required=True)
+parser.add_argument("--L1", help="transfer languages (split with comma for multiple ones)", type=str, required=False)
+parser.add_argument("--L2", help="test languages", type=str, required=True)
+parser.add_argument("--mode", help="usage mode", type=str,
+    choices=['train','test','test-dev','draw-dev','test-dev-ensemble','test-ensemble','test-two-ensemble','test-three-ensemble',
+    'test-all-ensemble'], default='', required=True)
+parser.add_argument("--setting", help="data setting", type=str, choices=['original','swap','low',], default='original')
+parser.add_argument("--modelpath", help="path to store the models", type=str, default='./models')
+parser.add_argument("--figurepath", help="path to store the output attention figures", type=str, default='./figures')
+parser.add_argument("--outputpath", help="path to store the inflected outputs on the test set", type=str, default='./outputs')
+parser.add_argument("--notest", help="do not use the test set at all", action="store_true")
+parser.add_argument("--testset", help="path to different test set", type=str, required=False)
+parser.add_argument("--outputfile", help="path to store the inflected outputs", type=str, required=False)
+parser.add_argument("--use_hall", help="whether to use a hallucinated dataset (def: False)", action="store_true")
[…]

### 2022-05-10 inflection/test_augmentation.py

@@ -1,0 +1,43 @@
+import os
+import time
+
+languages_0 = ["azeri","bengali","crimean-tatar"]
+languages_1 = ["karelian","kashubian","maltese"]
+languages_2 = ["middle-high-german","north-frisian","occitan"]
+languages_3 = ["old-church-slavonic","pashto","tatar","livonian"]
+
+languages = languages_3
+
+print("start time:", time.time())
+
+progress = 0
+max_progress = len(languages * 3)
+progress_bar = "[" + "".join([" "] * max_progress) + "]"
+
+for language in languages:
+    print(f'Working on {language}, regular')
+    os.system(f'mv sigmorphon_data/{language}-hall-regular sigmorphon_data/{language}-hall')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-regular.log 2>&1')
+    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-regular')
+    os.system(f'mv models/{language} models/{language}-hall-regular')
+    progress += 1
+    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
+    print(progress_bar)
+
+    print(f'Working on {language}, ngram')
+    os.system(f'mv sigmorphon_data/{language}-hall-ngram sigmorphon_data/{language}-hall')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-ngram.log  2>&1')
+    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-ngram')
+    os.system(f'mv models/{language} models/{language}-hall-ngram')
+    progress += 1
+    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
+    print(progress_bar)
+
+    print(f'Working on {language}, smart')
+    os.system(f'mv sigmorphon_data/{language}-hall-smart sigmorphon_data/{language}-hall')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-smart.log  2>&1')
+    os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-smart')
+    os.system(f'mv models/{language} models/{language}-hall-smart')
+    progress += 1
[…]

### 2022-05-11 tex/paper.tex
...
paper progress

@@
 \usepackage{float}
+\usepackage{verbatim}
+\usepackage{listings}
+\usepackage{fancyvrb}
+\usepackage{pmboxdraw}
+\usepackage{subcaption}
+
 \bibliographystyle{plain}
@@
 Given the demonstrated ability of GANs to produce photorealistic, yet completely contrived images, they are potentially ideal for such a task.
+The experiments detailed in this paper attempt to produce a technique for generating fake word stems that provide more relevant information to the inflectional model from Anastasopoulos and Neubig, 2019 \cite{CMU}, thereby increasing the accuracy of its inflections.
+By modeling the graphotactics of the target language using a GAN, it should be possible to produce strings that more accurately depict possible character sequences.
 
@@
 The data for each language was gathered from their respective Wikipedia.
-Only the "train-low" sets were used for training.
-These datasets has only 100 examples, with each containing a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the "train-low" sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}
+Only the ``train-low'' sets were used for training.
+These datasets has only 100 examples, with each containing a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the ``train-low'' sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}
 
       To produce training data for the GAN, base forms were aligned with inflected forms using a technique developed by Mans Hulden called Chinese restaurant process alignment \cite{crpalign}.
-Based on the alignment, a series of likely stems are generated using code from Anastasopoulos and Neubig, 2019 \cite{CMU}; as most of the languages tested use primarily suffixational inflection, the first of these "likely" stems was assumed to be the true stem and was included in the language's training set as an example of graphotactic compliance.
+Based on the alignment, a series of likely stems are generated using code from Anastasopoulos and Neubig, 2019 \cite{CMU}; as most of the languages tested use primarily suffixational inflection, the first of these ``likely'' stems was assumed to be the true stem and was included in the language's training set as an example of graphotactic compliance.
 
@@
 Some had zeroes (representing null characters) in the middle, others filled the entire 10 available characters (which most real stems do not).
-To combat this, model output strings were "cleaned".
+To combat this, model output strings were ``cleaned''.
 Strings were cut off at the first zero from the left (all languages were left-to-right), if a character was repeated more than twice consecutively, it was collapsed to just two, and if the length of the stem was longer than the real stem it was replacing, it was shortened to a matching length.
@@
     \subsection{Testing}
+      The inflectional model from Anastasopoulos and Neubig, 2019 \cite{CMU} was used as a benchmark.
+For each language, three sets of ``hallucinated'' data were generated.
+The first used the random character selection method from Anastasopoulos and Neubig, 2019 \cite{CMU}, the second was the GAN produced set, and the third was produced by a simple trigram model trained on same 100 example as the GAN.
+
+      The model was run without cross-lingual transfer.
+All other parameters were left at their defaults.
+The number of epochs used by the training routine varied programmatically according to perceived accuracy.
 
   \section{Results}
+    \subsection{GAN Training}
+      Models generally fell into two camps when training.
+With some, the generator loss quickly rose to 1 (the maximum) while the discriminator loss simultaneously fell to -1 (the minimum) (Fig.
+\ref{fig:kashubianloss}).
+With the others, generator loss fluctuated rapidly between 0 and 1, while the discriminator loss fluctuated rapidly between -1 and 0 (Fig.
+\ref{fig:azeriloss}).
+
+      \begin{figure}[H]
+        \centering
+        \begin{subfigure}{.5\textwidth}
+          \centering
+          \includegraphics[width=0.8\linewidth]{loss_plots/kashubian.pdf}
+          \caption{Loss pattern 1}
+          \label{fig:kashubianloss}
+        \end{subfigure}%
+        \begin{subfigure}{.5\textwidth}
+          \centering
+          \includegraphics[width=0.8\linewidth]{loss_plots/azeri.pdf}
+          \caption{Loss pattern 2}
+          \label{fig:azeriloss}
+        \end{subfigure}
+        \caption{Examples of each loss pattern}
+        \label{fig:loss}
+      \end{figure}
+
+      In the first case, it seems that the model is learning for the first few epochs but quickly exhausts its potential.
+This is evident in the sample strings generated as well.
+As an example, for the first 100 or so epochs, the Kashubian model generated strings that were mostly a single character: ``şşşşşşşşşş''.
+But after about 300 epochs, string began to resemble stems with a reasonable number of zeroes (null characters) at the end: ``dümç000000''.
+
+      In the second case, the model is able to return to these more realistically structured strings occcasionally (denoted by the fluctuations), but it is not able to produce these strings with any consistency.
+
+    \subsection{Performance}
+      Neither the GAN nor the trigram model were able to consistently produce data that was more informative than the random strings (Fig.
+\ref{fig:accuracy}).
+For all languages except North Frisian and Occitan, training on the randomly augmented set resulted in the highest accuracy.
+The models trained on the trigram augmented set often performed similarly to those trained on the random set, having identical accuracy in Occitan and slighly higher accuracy in North Frisian.
+
+      No model trained on GAN augmented data achieved higher than 18\% accuracy, and in 10 of 13 cases, these models were less than 10\% accurate.
+In all cases, training on the 100 example ``train-low'' set alone resulted in a more accurate model than training on both the ``train-low'' and GAN augmented sets; on average, adding GAN augmented data resulted in a model that was only one fifth as accurate as models trained on unuagmented data.
+
+      \begin{figure}[H]
+        \center
+        \begin{tabular}{lrrrr}
+          \toprule
+          Language & Unaugmented & Random & Trigram & GAN \\
+          \midrule
+          Azeri & 0.10 & \textbf{0.31} & 0.25 & 0.00 \\
+          Bengali & 0.25 & \textbf{0.56} & 0.55 & 0.03 \\
+          Crimean Tatar & 0.21 & \textbf{0.63} & 0.62 & 0.11 \\
+          Karelian & 0.34 & \textbf{0.54} & 0.38 & 0.02 \\
+          Kashubian & 0.46 & \textbf{0.56} & 0.30 & 0.14 \\
+          Livonian & 0.12 & \textbf{0.32} & 0.26 & 0.07 \\
+          Maltese & 0.24 & \textbf{0.32} & 0.19 & 0.00 \\
+          Middle High German & 0.62 & \textbf{0.68} & 0.66 & 0.18 \\
+          North Frisian & 0.15 & 0.16 & \textbf{0.19} & 0.00 \\
+          Occitan & 0.26 & \textbf{0.78} & \textbf{0.78} & 0.01 \\
+          Old Church Slavonic & 0.24 & \textbf{0.44} & 0.21 & 0.08 \\
+          Pashto & 0.10 & \textbf{0.40} & 0.36 & 0.03\\
+          Tatar & 0.27 & \textbf{0.71} & 0.61 & 0.03\\
+          \midrule
+          Average & 0.26 & \textbf{0.49} & 0.41 & 0.05\\
+          \bottomrule
+        \end{tabular}
+        \caption{Accuracy of resultant inflectional models using various data augmentation methods}
+        \label{fig:accuracy}
+      \end{figure}
+
+      On average Levenshtein distance calculations follow a similar pattern to that of model accuracy; however, this metric occasionally favors the models trained on trigram augmented data (Fig.
+\ref{fig:lev}).
+Additionally, in the case of North Frisian, a particularly difficult language to inflect (based on the accuracy results), the model trained on just the 100 original examples had a slightly lower average Levenshtein distnace.
+
+      \begin{figure}[H]
+        \center
+        \begin{tabular}{lrrrr}
+          \toprule
+          Language & Unaugmented & Random & Trigram & GAN \\
+          \midrule
+          Azeri & 3.13 & \textbf{1.76} & 2.02 & 5.42 \\
+          Bengali & 2.66 & \textbf{0.81} & 0.95 & 4.59 \\
+          Crimean Tatar & 2.34 & 0.54 & \textbf{0.50} & 3.18 \\
+          Karelian & 1.74 & 1.94 & \textbf{1.46} & 4.10 \\
+          Kashubian & 1.44 & \textbf{1.22} & \textbf{1.22} & 2.78 \\
+          Livonian & 3.91 & \textbf{2.23} & 2.55 & 4.78 \\
+          Maltese & 2.31 & \textbf{1.51} & 1.91 & 5.29 \\
+          Middle High German & 0.80 & \textbf{0.46} & 0.60 & 1.92 \\
+          North Frisian & \textbf{3.12} & 3.21 & 3.54 & 7.88 \\
+          Occitan & 2.19 & \textbf{0.53} & 0.57 & 5.78 \\
+          Old Church Slavonic & 2.34 & \textbf{1.09} & 1.94 & 3.00 \\
+          Pashto & 2.53 & \textbf{1.25} & 1.34 & 4.79\\
+          Tatar & 2.19 & \textbf{0.50} & 0.62 & 5.52\\
+          \midrule
+          Average & 2.36 & \textbf{1.31} & 1.48 & 4.54\\
+          \bottomrule
+        \end{tabular}
+        \caption{Average Levenshtein distance (minimum number of elementary string operations to go from prediction to label) of resultant inflectional models using various data augmentation methods}
+        \label{fig:lev}
+      \end{figure}
   \section{Discussion}
 
-  REMEMBER TO INCLUDE LINKS TO ALL CODE CREATED AND USED
+  TODO: REMEMBER TO INCLUDE LINKS TO ALL CODE CREATED AND USED
   \bibliography{sources}

### 2022-05-11 inflection/myutil.py

@@ -32,7 +32,7 @@ def read_data(filename):
         if l:
             inputs.append(list(l[0]))
             outputs.append(list(l[1]))
-            tags.append(re.split('\W+', l[2]))
+            tags.append(re.split('\W+', l[-1]))
     return inputs, outputs, tags
 
 def read_test_data(filename):

### 2022-05-11 inflection/test_no_aug.py

@@ -1,0 +1,23 @@
+import os
+import time
+
+languages_0 = ["azeri","bengali","crimean-tatar"]
+languages_1 = ["karelian","kashubian","maltese"]
+languages_2 = ["middle-high-german","north-frisian","occitan"]
+languages_3 = ["old-church-slavonic","pashto","tatar","livonian"]
+
+languages = languages_0 + languages_1 + languages_2 + languages_3
+
+print("start time:", time.time())
+
+progress = 0
+max_progress = len(languages)
+progress_bar = "[" + "".join([" "] * max_progress) + "]"
+
+for language in languages:
+    print(f'Working on {language}, unaugmented')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train > train-{language}-no-augmentation.log 2>&1')
+    os.system(f'mv models/{language} models/{language}-no-augmentation')
+    progress += 1
+    progress_bar = "[" + "".join(([u"\u2588"] * progress) + ([" "] * (max_progress - progress))) + "]"
+    print(progress_bar)

### 2022-05-11 tex/paper.tex
discussion section done

@@
   \section{Discussion}
+    \subsection{Analysis}
+      GAN based augmentation, using the techniques described, is not a good option for creating artificial training data for the inflection model.
+It seems as though 100 examples is simply insufficient for the GAN to learn properly.
+Though there was initially concern that GAN based augmentation could only produce redundant examples, providing no additional information, the fact that it results in worse inflection performance than using unaugmented data means that the GAN is providing novel, yet misleading, information.
 
-  TODO: REMEMBER TO INCLUDE LINKS TO ALL CODE CREATED AND USED
+      Observation of the artificial datasets reveals obvious flaws in the distribution of characters.
+For example, in the case of Azeri, the GAN augmented dataset contains 165 ``ü'' characters per 100 examples, while the unaugmented, randomly augmented, and trigram augmented datasets contain 44, 35, and 28 ``ü'' characters respectively.
+Similar flaws can be observed in the GAN augmented datasets for each language.
+These human-recognizable flaws could likely be averted using some sort of penalty based on relative character frequency in the training data, but there likely exist equally detrimental flaws that cannot be easily observed and would therefore be more difficult to penalize.
+The relative success of the trigram model suggests that many of these flaws can be avoided by using a less complex (or statistical) model that requires less data to function properly.
+However, given that random augmentation outperforms all other methods tested, it seems there is little reason to pursue such methods.
+
+      Anastasopoulos and Neubig's method, random augmentation, remains the best method for creating informative yet nondeceptive artificial examples \cite{CMU}.
+The randomness indicates to the inflection model that the stem varies freely and has no bearing on the inflection.
+However, this is, of course, not always the case.
+Though many languages have ``regular'' inflectional paradigms (adding ``-ed'' for past tense in English), there are also many irregular forms, influenced by the stem (``run'' [+past] = ``ran'').
+In these cases, the stem must be taken into consideration to predict the correct inflectional morpheme.
+This means that an ideal informed (not entirely random) model should be able to produce more accurate and informative data than the random augmentor.
+
+    \subsection{Future Work}
+      Based on the conclusions above, there are two avenues of research that are begging to be pursued.
+The first involves modifying the task and model of Anastasopoulos and Neubig, 2019 \cite{CMU} to work only with the non-stem characters in each example (those which are not shared between the lemma and inflected form).
+Working on the assumptions made by random augmentation (that the stem has no bearing on inflection), such a model should perform similarly to one using random augmentation if it is trained for an equal number of iterations.
+
+      The second avenue for future research involves rejecting the assumption made by random augmentation and instead assuming a finite number of inflectional paradigms, so that inflection may be turned into a classification task.
+Lemmas in the training set would first be categorized into paradigms; then, a classification model would be trained using only the lemmas as $X$ and the paradigm's ID as $y$.
+Each inflectional paradigm corresponds to a function $f(T)$ where $T$ is the set of morphological tags for the inflected form requested.
+
+    \subsection{Conclusion}
+      The emergence of new machine learning technologies are an opportunity to revisit attempts at low-resource language preservation and support.
+As language speakers and language learners, we know that a dataset of thousands of examples is not a necessary prerequistite for learning the inflectional paradigms of natural language.
+There is no doubt that small datasets like those used in the experiments above will one day be sufficient for inflection automation with human-like accuracy.
+
+      TODO INCLUDE LINKS TO CODE ETC
   \bibliography{sources}
-
 \end{document}

### 2022-05-11 inflection/test_augmentation.py
reorganization

@@ -17,7 +17,7 @@ progress_bar = "[" + "".join([" "] * max_progress) + "]"
 for language in languages:
     print(f'Working on {language}, regular')
     os.system(f'mv sigmorphon_data/{language}-hall-regular sigmorphon_data/{language}-hall')
-    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-regular.log 2>&1')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train_logs/train-{language}-regular.log 2>&1')
     os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-regular')
     os.system(f'mv models/{language} models/{language}-hall-regular')
     progress += 1
@@ -26,7 +26,7 @@ for language in languages:
 
     print(f'Working on {language}, ngram')
     os.system(f'mv sigmorphon_data/{language}-hall-ngram sigmorphon_data/{language}-hall')
-    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-ngram.log  2>&1')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train_logs/train-{language}-ngram.log  2>&1')
     os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-ngram')
     os.system(f'mv models/{language} models/{language}-hall-ngram')
     progress += 1
@@ -35,7 +35,7 @@ for language in languages:
 
     print(f'Working on {language}, smart')
     os.system(f'mv sigmorphon_data/{language}-hall-smart sigmorphon_data/{language}-hall')
-    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train-{language}-smart.log  2>&1')
+    os.system(f'python inflection.py --datapath sigmorphon_data --L2 {language} --mode train --use_hall > train_logs/train-{language}-smart.log  2>&1')
     os.system(f'mv sigmorphon_data/{language}-hall sigmorphon_data/{language}-hall-smart')
     os.system(f'mv models/{language} models/{language}-hall-smart')
     progress += 1

### 2022-05-11 MNIST_GAN/align.py
reorg continued

@@ -1,96 +1,0 @@
-# Simple class for learning an alignment of strings, MED-style.
-# Weights are learned by a Chinese Restaurant Process sampler
-# that weights single alignments x:y in proportion to how many times
-# such an alignment has been seen elsewhere out of all possible alignments.
-
-# Licensed under the Apache License, Version 2.0 (the "License");
-# you may not use this file except in compliance with the License.
-# You may obtain a copy of the License at
-#     http://www.apache.org/licenses/LICENSE-2.0
-
-# Usage:
-# Align(wordpairs) <= wordpairs is an iterable of 2-tuples containing strings as iterables
-# The resulting Align.alignedpairs is a list of aligned 2-tuples
-
-# Relies on C-code in libalign.so built from align.c through ctypes.
-# Author: Mans Hulden
-# MH20151102
-# Last modified 20200422
-
-import itertools
-from ctypes import *
-
-libalign = cdll.LoadLibrary('./libalign.so')
-
-libalign_add_int_pair = libalign.add_int_pair
-libalign_clear_counts = libalign.clear_counts
-libalign_initial_align = libalign.initial_align
-libalign_crp_train = libalign.crp_train
-libalign_crp_align = libalign.crp_align
-libalign_med_align = libalign.med_align
-
-libalign_getpairs_init = libalign.getpairs_init
-libalign_getpairs_init.restype = c_void_p
-libalign_getpairs_in = libalign.getpairs_in
-libalign_getpairs_in.restype = POINTER(c_int)
-libalign_getpairs_out = libalign.getpairs_out
-libalign_getpairs_out.restype = POINTER(c_int)
-libalign_getpairs_advance = libalign.getpairs_advance
-libalign_getpairs_advance.restype = c_void_p
-libalign_align_init = libalign.align_init
-libalign_align_init.restype = None
-
-class Aligner:
-
-    def __init__(self, wordpairs, align_symbol = ' ', iterations = 10, burnin = 1, lag = 1, mode = 'crp'):
-        s = set()
-        for wl, wr in wordpairs:
-            s |= {a for a in wl}
-            s |= {a for a in wr}
-        self.symboltoint = dict(zip(s, range(1,len(s)+1)))
-        self.inttosymbol = {v:k for k, v in self.symboltoint.items()}
-        self.inttosymbol[0] = align_symbol
-        ## Map stringpairs to -1 terminated integer sequences ##
-        intpairs = []
-        for i, o in wordpairs:
[…]

### 2022-05-11 word_gan/auto_augmentor.py

@@ -1,8 +1,6 @@
 import os
 
 languages = ["azeri","bengali","crimean-tatar","ingrian","karelian","kashubian","livonian","maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
-languages = ["maltese","middle-high-german","north-frisian","occitan","old-church-slavonic","pashto","tatar"]
-languages = ["ingrian"]
 for language in languages:
     print(f'Working on {language}, regular')
     os.system(f'python augment_regular.py sigmorphon_data {language} --examples 10000')

### 2022-05-11 word_gan/losses_impl.py

@@ -1,1101 +1,0 @@
-# coding=utf-8
-# Copyright 2022 The TensorFlow GAN Authors.
-#
-# Licensed under the Apache License, Version 2.0 (the "License");
-# you may not use this file except in compliance with the License.
-# You may obtain a copy of the License at
-#
-#     http://www.apache.org/licenses/LICENSE-2.0
-#
-# Unless required by applicable law or agreed to in writing, software
-# distributed under the License is distributed on an "AS IS" BASIS,
-# WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
-# See the License for the specific language governing permissions and
-# limitations under the License.
-
-"""Losses that are useful for training GANs.
-
-The losses belong to two main groups, but there are others that do not:
-1) xxxxx_generator_loss
-2) xxxxx_discriminator_loss
-
-Example:
-1) wasserstein_generator_loss
-2) wasserstein_discriminator_loss
-
-Other example:
-wasserstein_gradient_penalty
-
-All losses must be able to accept 1D or 2D Tensors, so as to be compatible with
-patchGAN style losses (https://arxiv.org/abs/1611.07004).
-
-To make these losses usable in the TF-GAN framework, please create a tuple
-version of the losses with `losses_utils.py`.
-"""
-
-import tensorflow as tf
-
-
-def _to_float(tensor):
-  return tf.cast(tensor, tf.float32)
-
-
-# Wasserstein losses from `Wasserstein GAN` (https://arxiv.org/abs/1701.07875).
-def wasserstein_generator_loss(
-    discriminator_gen_outputs,
-    weights=1.0,
-    scope=None,
-    loss_collection=tf.compat.v1.GraphKeys.LOSSES,
-    reduction=tf.compat.v1.losses.Reduction.SUM_BY_NONZERO_WEIGHTS,
-    add_summaries=False):
-  """Wasserstein generator loss for GANs.
-
-  See `Wasserstein GAN` (https://arxiv.org/abs/1701.07875) for more details.
-
-  Args:
-    discriminator_gen_outputs: Discriminator output on generated data. Expected
-      to be in the range of (-inf, inf).
-    weights: Optional `Tensor` whose rank is either 0, or the same rank as
-      `discriminator_gen_outputs`, and must be broadcastable to
-      `discriminator_gen_outputs` (i.e., all dimensions must be either `1`, or
-      the same as the corresponding dimension).
-    scope: The scope for the operations performed in computing the loss.
[…]

### 2022-05-11 word_gan/train.py

@@ -1,312 +1,0 @@
-import numpy as np
-import tensorflow as tf
-import tensorflow.keras as keras
-from tensorflow.keras import layers
-from keras.preprocessing import sequence
-from sklearn.model_selection import train_test_split
-import pandas as pd
-
-import align
-import argparse
-import codecs
-import os, sys
-from random import random, choice
-import re
-import glob
-import matplotlib.pyplot as plt
-import time
-from losses_impl import *
-from keras import backend
-
-
-from IPython.utils import io
-max_stem_length = 10
-def read_data(filename):
-    with codecs.open(filename, 'r', 'utf-8') as inp:
-        lines = inp.readlines()
-    inputs = []
-    outputs = []
-    tags = []
-    for l in lines:
-        l = l.strip().split('\t')
-        if l:
-            inputs.append(list(l[0].strip()))
-            outputs.append(list(l[1].strip()))
-            tags.append(re.split('\W+', l[2].strip()))
-    return inputs, outputs, tags
-
-def find_good_range(a,b):
-	mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
-	if sum(mask) == 0:
-		# Some times the alignment is off-by-one
-		b = [' '] + b
-		mask = [(a[i]==b[i] and a[i] != u" ") for i in range(len(a))]
-	ranges = []
-	prev = False
-	for i,k in enumerate(mask):
-		if k and prev:
-			prev = True
-		elif k and not prev:
-			start = i
-			prev = True
-		elif prev and not k:
-			end = i
-			ranges.append((start, end))
-			prev = False
-		elif not prev and not k:
-			prev = False
-	if prev:
-		ranges.append((start,i+1))
-	ranges = [c for c in ranges if c[1]-c[0]>2]
-	return ranges
-def generate_stem():
-	return "___"
-
-def get_chars(l):
-    flat_list = [char for word in l for char in word]
-    return list(set(flat_list))
-def best_range(ranges):
-    longest_length = 0
-    longest_index = 0
-    for i,r in enumerate(ranges):
-        length = r[1] - r[0]
-        if length > longest_length:
-            longest_length = length
-            longest_index = i
-    return ranges[i]
-
-def augment(input_path):
-    inputs,outputs,tags = np.array(read_data(input_path), dtype=object)
-    temp = [(''.join(inputs[i]), ''.join(outputs[i])) for i in range(len(outputs))]
-    aligned = align.Aligner(temp).alignedpairs
[…]

### 2022-05-11 Paper/paper.tex
reog continued

--- 2022-05-11 tex/paper.tex
@@
 
-      TODO INCLUDE LINKS TO CODE ETC
+    \section*{Code and Data}
+    \subsection*{Written}
+    \subsection*{Referenced}
+    \begin{enumerate}
+      \item Code from Anastasopoulos and Neubig, 2019: \url{https://github.com/antonisa/inflection}
+      \item Stem alignment code from Mans Hulden: \url{https://github.com/mhulden/crpalign}
+      \item GAN training routine from Géron: \url{https://github.com/ageron/handson-ml2/blob/master/17_autoencoders_and_gans.ipynb}
+      \item Data for the SIGMORPHON 2019 shared task: \url{https://github.com/sigmorphon/2019}
+      \item Wasserstein loss implementation: \url{https://machinelearningmastery.com/how-to-implement-wasserstein-loss-for-generative-adversarial-networks}
+    \end{enumerate}
   \bibliography{sources}

### 2022-05-11 Paper/paper.tex
fixed mistakes

@@
 
-      To perform this hallucination, they aligned the lemma with its inflected form, extracted the stem, and generated new artificial examples by replacing this stem with randomly generated strings (in the language's alphabet) of equal length.\footnote{The alignment process assumes that the lemma and inflected form share a common substring.} Though a seemingly haphazard method of data augmentation, this approach allowed for an additional 10\% accuracy, on average, when tested against versions of the model that only used cross-lingual transfer.
+      To perform this hallucination, they aligned the lemma with its inflected form, extracted the stem, and generated new artificial examples by replacing this stem with randomly generated strings (in the language's alphabet) of equal length.\footnote{The alignment process assumes that the lemma and inflected form share a common substring.} Though this random substitution may seem haphazard, the approach allowed for an additional 10\% accuracy, on average, when tested against versions of the model that only used cross-lingual transfer.
 
@@
     \subsection{GANs for Data Augmentation}
-      Although GANs are most popularly used for domain transfer, the same basic architecture is also a good candidate for a data augmentation strategy called hallucination in which new (fake) training examples based on a small number of existing (real) examples.
+      Although GANs are most popularly used for domain transfer, the same basic architecture is also a good candidate for a data augmentation strategy called hallucination in which new (fake) training examples are created based on a small number of existing (real) examples.
 
@@
 Only the ``train-low'' sets were used for training.
-These datasets has only 100 examples, with each containing a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the ``train-low'' sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}
+These datasets have only 100 examples, and each example contains a lemma (base form), an inflected form, and a list of the morphological categories associated with the inflected form.\footnote{Although the ``train-low'' sets do occasionally have 1000 examples, those corresponding to the languages used in this experiment have only 100.}
 
@@
 \ref{fig:lev}).
-Additionally, in the case of North Frisian, a particularly difficult language to inflect (based on the accuracy results), the model trained on just the 100 original examples had a slightly lower average Levenshtein distnace.
+Additionally, in the case of North Frisian, a particularly difficult language to inflect (based on the accuracy results), the model trained on just the 100 original examples had a slightly lower average Levenshtein distance.
 
@@
     \subsection*{Written}
+      All code can be found in this Github repo: \url{https://github.com/isaacwasserman/ml-final-project}.\\
+      \\Here are some files of particular importance:
+      \begin{enumerate}
+        \item GAN training notebook: \url{https://github.com/isaacwasserman/ml-final-project/blob/main/word_gan/word_gan.ipynb}
+        \item Augmentation script: \url{https://github.com/isaacwasserman/ml-final-project/blob/main/word_gan/augment_smart.py}
+        \item Augmented datasets: \url{https://github.com/isaacwasserman/ml-final-project/tree/main/inflection/augmented_data}
+      \end{enumerate}
     \subsection*{Referenced}
